### 2009-11-10 doc/manuals/chelonia/chelonia-cli.tex
documenting the remaining methods of the chelonia cli

\subsubsection{move} % (fold)
\label{ssub:move}
With the \texttt{move} or \texttt{mv} method it is possible to move a file or collection within the namespace of chelonia (including renaming the entry). The source path and the target path should be specified as Logical Names
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia list $<$sourceLN$>$ $<$targetLN$>$}
\end{shaded}

@@

>>>>

\subsubsection{move} % (fold)
\label{ssub:move}
With the \texttt{move} or \texttt{mv} method it is possible to move a file or collection within the namespace of chelonia (including renaming the entry). The source path and the target path should be specified as Logical Names
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia move $<$sourceLN$>$ $<$targetLN$>$}
\end{shaded}

@@

\subsubsection{policy} % (fold)
\label{ssub:policy}

With the \texttt{policy} or \texttt{pol} method it is possible to modify the policy of the entry
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia policy $<$LN$>$ $<$changeType$>$ $<$identity$>$ $<$action list$>$}   
\end{shaded}

The possible values of `changeType' are `set' (sets the action list to the given user overwriting the old one), `change' (modify the current action list with adding and removing actions) and `clear' (clear the action list of the given user).

The `identity' could be currently three things: the DN of a user; the name of a VO (with the syntax: `VOMS:$<$VO name$>$'); or `ALL' for all users.

The `action list' is a list of actions prefixed with `+' or `-', e.g. `+read +addEntry -delete'.

These are the actions which can be used for access control:
\begin{itemize}
    \item \emph{read}: user can get the list of entries in the collection; user can download the file
    \item \emph{addEntry}: user can add a new entry to the collection;
    \item \emph{removeEntry}: user can remove any entry from the collection 
    \item \emph{delete}: user can delete the collection if it is empty; user can delete a file
    \item \emph{modifyPolicy}: user can modify the policy of the file/collection
    \item \emph{modifyStates}: user can modify some special metadata of the file/collection (close the collection, change the number of needed replica of the file)
    \item \emph{modifyMetadata}: user can modify the arbitrary metadata section of the file/collection (these are property-value pairs)
\end{itemize}

There is an implicit default policy: the owner always has all the rights.
Checking the `stat' of new collections:
\begin{verbatim}
$ chelonia stat /newcoll
'/newcoll': found
  states
    closed: no
  entry
    owner: /C=HU/O=NIIF CA/OU=GRID/OU=NIIF/CN=Nagy Zsombor
    GUID: 41CBD461-09BE-46FD-8A1B-767C7D427AF9
    type: collection
  parents
    0/newcoll: parent
  timestamps
    created: 1257435820.26
  entries
    thing: A63658B4-2C6E-46A3-8238-7D291F8F81C2
\end{verbatim}
shows no policies, but it shows the owner. This collection has no additional policies just the default one: the owner can do anything, noone else can do anything.

Let's set it in a way that all users can read the contents of this collection:
\begin{verbatim}
$ chelonia policy /newcoll change ALL +read
Setting action list of '/newcoll' for user ALL to +read: set.
$ chelonia stat /newcoll
'/newcoll': found
  [...]
  policy
    ALL: +read
  [...]
\end{verbatim}

Then we can set that all the members of the knowarc VO would be able to add entries to this collection:
\begin{verbatim}
$ chelonia policy /newcoll change VOMS:knowarc +addEntry
Setting action list of '/newcoll' for user VOMS:knowarc to +addEntry: set.
$ chelonia stat /newcoll
'/newcoll': found
  [...]
  policy
    ALL: +read
    VOMS:knowarc: +addEntry
  [...]
\end{verbatim}

And for example we can set a specific user to be able to remove entries from this collections:
\begin{verbatim}
$ chelonia policy /newcoll change \
    "/C=HU/O=NIIF CA/OU=GRID/OU=NIIF/CN=TestUser" +removeEntry
Setting action list of '/newcoll'
    for user /C=HU/O=NIIF CA/OU=GRID/OU=NIIF/CN=TestUser to +removeEntry: set.
$ chelonia stat /newcoll'/newcoll': found
  [...]
  policy
    /C=HU/O=NIIF CA/OU=GRID/OU=NIIF/CN=TestUser: +removeEntry
    ALL: +read
    VOMS:knowarc: +addEntry
  [...]
\end{verbatim}

% subsubsection policy (end)

\subsubsection{unlink} % (fold)
\label{ssub:unlink}

With the \texttt{unlink} method it is possible to remove a file or collection just from its parent collection without removing the file or collection itself.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unlink $<$LN$>$}   
\end{shaded}

If there is a file called `/newcoll/thing', it is in the listing of the `/newcoll' collection:
\begin{verbatim}
$ chelonia list /newcoll
'/newcoll': collection
  thing <file>
\end{verbatim}    
The file is in the entries of the collection:
\begin{verbatim}
$ chelonia stat /newcoll
'/newcoll': found
  entries
    thing: A63658B4-2C6E-46A3-8238-7D291F8F81C2
  [...]
\end{verbatim}

It is possible the `stat' the file with the Logical Name `/newcoll/thing':
\begin{verbatim}
jim:~ zsombor$ chelonia stat /newcoll/thing
'/newcoll/thing': found
  states
    checksumType: md5
    neededReplicas: 3
    size: 6
    checksum: a0186a90393bd4a639a1ce35d8ef85f6
  [...]
\end{verbatim}

Now with the `unlink' method it is possible to remove the file from the `/newcoll' collection, but not from the system:
\begin{verbatim}
$ chelonia unlink /newcoll/thing
Unlinking '/newcoll/thing': unset
\end{verbatim}

Now the file is not in the collection anymore:
\begin{verbatim}
$ chelonia list /newcoll
'/newcoll': collection
    empty.
$ chelonia stat /newcoll/thing
'/newcoll/thing': not found
\end{verbatim}

But with the GUID of the file, it can still be accessed:
\begin{verbatim}
$ chelonia stat A63658B4-2C6E-46A3-8238-7D291F8F81C2
'A63658B4-2C6E-46A3-8238-7D291F8F81C2': found
  states
    checksumType: md5
    neededReplicas: 3
    size: 6
    checksum: a0186a90393bd4a639a1ce35d8ef85f6
  [...]
\end{verbatim}
% subsubsection unlink (end)

\subsubsection{credentialDelegation} % (fold)
\label{ssub:credentialdelegation}
With the \texttt{credentialDelegation} or \texttt{cre} method it is possible to delegate credentials to the Bartender.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia credentialDelegation}   
\end{shaded}
% subsubsection credentialdelegation (end)

\subsubsection{removeCredentials} % (fold)
\label{ssub:removecredentials}
With the \texttt{removeCredentials} or \texttt{rem} method it is possible to remove the previously delegated credentials.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia removeCredentials}   
\end{shaded}
% subsubsection removecredentials (end)

\subsubsection{makeMountPoint} % (fold)
\label{ssub:makemountpoint}
With the \texttt{makeMountPoint} or \texttt{makemount} method it is possible to create a mount point within the namespace of Chelonia which points to a GridFTP server.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia makeMountPoint $<$LN$>$ $<$URL$>$}   
\end{shaded}

The `LN' is the requested Logical Name for the mount point, the `URL' points to the GridFTP server.
% subsubsection makemountpoint (end)

\subsubsection{unmakeMountPoint} % (fold)
\label{ssub:unmakemountpoint}
With the \texttt{unmakeMountPoint} or \texttt{unmount} method it is possible to remove a previously created mount point.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unmakeMountPoint $<$LN$>$}   
\end{shaded}

The `LN' is the Logical Name of the mount point.
% subsubsection unmakemountpoint (end)
